\documentclass[12pt]{article}
 
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
 
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
 
\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
 
\begin{document}
 
\title{Test 2-Rewrite}
\author{Ed Sanchez\\ 
Math 200: Techniques of Mathematical Proofs}
 
\maketitle
 
\begin{problem}{1}
\text{ }\\
Claim: Prove that if A is a well ordered set and B is a nonempty subset of A, then B is well ordered
\end{problem}
 
\begin{proof}
Let A be a well ordered set and B be a nonempty subset of B. In Order for B to be well ordered, every subset must have a least element. It follows that $S\subseteq B \subseteq A$ where S is a nonempty subset of B. Since A is well ordered, S must have a least element. Therefore, B is well ordered since each subset of B has a least element
\end{proof}
 
\begin{problem}{2}
\text{ }\\
 Claim: Prove there exist no positive integer x such that $2x < x^2 < 3x$.
\end{problem}
\begin{proof}
Assume, via contradiction that there exist a positive integer x that satisfies $2x < x^2 < 3x$. Thus, there is an x that can satisfy $2x < x^2$ and $x^2 < 3x$. Yet, x will only satisfy $2x<x^2$ when $x \geq 3$ and will only satisfy $x^2 < 3x$ when $x \leq 2$. Therefore, our assumption that there exist a positive integer x that satisfies $2x < x^2 < 3x$ was false so there exist no positive integer x such that $2x < x^2 < 3x$
\end{proof} 

\begin{problem}{3}
\text{ }\\
 Claim: Prove that $2^n > n^3$ for every integer $n\geq10$
\end{problem}
\begin{proof}
Assume that P(n): $2^n > n^3$. For the base case, use n=10. Observe the following. 
\begin{align}
\nonumber
1024&>1000
\end{align}
Inductive Step: Assume that P(k): $2^k > k^3$ for a positive integer $k\geq10$. We want to show that  $2^{k+1} > (k+1)^3$ for $(k+1)\geq10$.
\begin{align}
\\ \nonumber
2^{k+1}&=2 * 2^{k}
\\ \nonumber
&>2*k^3
\\ \nonumber 
&= k^3+k^3
\\ \nonumber 
k^3&=k * k^2 
\\ \nonumber
&>10k^{2}
\\ \nonumber
&= 3k^2+7k
\end{align}
Now, consider the following.
\begin{align}
\\ \nonumber
(k+1)^3&=k^3+3k^2+(3k+1)
\\ \nonumber
\end{align}
Plug in the base case,k=10, to find. 
\begin{align}
\\ \nonumber
3k+1 &< 7k
\\ \nonumber
31 &< 70
\end{align}
As desired. By the principle of Mathematical Induction, $2^n > n^3$ for every integer $n\geq10$
\end{proof} 

\begin{problem}{4}
\text{ }\\
 Claim: Suppose that $a_n$ is a sequence of real numbers defined recursively by $a_1=1,a_2=2,a_3=3$ and $a_n=2a_{n-1}-a_{n-3}$ for $n \geq 4$. Prove that $a_n=a_{n-1}+a_{n-2}$ for every integer $n \geq 3$.
\end{problem}
\begin{proof}
P(n): If $a_1=1,a_2=2,a_3=3$ and $a_n=2a_{n-1}-a_{n-3}$ for $n \geq 4$ then $a_n=a_{n-1}+a_{n-2}$ for every integer $n \geq 3$. To start, assume the base case is n=3. Thus, 
\begin{align}
\nonumber
a_3&= a_2 + a_1
\\\nonumber
3&= 2 + 1
\\\nonumber
\end{align}
This proofs the base case. \\
Inductive Step: For $i={1,2,...,k}, P(i): a_i=a_{i-1}+a_{i-2}$ for every $k \geq 3$. We show that $a_{k+1}=2a_{k}-a_{k-2}$
\begin{align}
\nonumber
a_{k+1}&=2a_{k}-a_{k-2}
\\\nonumber
&=a_{k}+a_{k}-a_{k-2}
\\\nonumber
&=a_{k}+a_{k}-a_{k}-a_{k-1}
\\\nonumber
&=a_{k-1}+a_{k+2}
\\\nonumber
\end{align}
which is the desired result. It shows that both $a_n$ functions are equivalent. By the Strong Principle of Mathematical Induction, If $a_1=1,a_2=2,a_3=3$ and $a_n=2a_{n-1}-a_{n-3}$ for $n \geq 4$ then $a_n=a_{n-1}+a_{n-2}$ for every integer $n \geq 3$.
\end{proof}


\end{document}
